\bfseries\large Phosphatidylinositol 4,5-bisphosphate regulates cilium transition zone maturation in \textit{Drosophila melanogaster}

### 2018-03-01 latex/paper.tex
Various edits

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[numbers]{natbib}
\usepackage[draft]{graphicx}  %% remove [draft] to compile with pictures
\graphicspath{{../figures/}}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

@@

\section{Discussion}
Cilia are essential for proper human development, and their disruption
can cause genetic disorders with severities ranging from congenital-
lethal \citep{}
to late onset \citep{}.
A large number of ciliopathies are associated with genes that encode for
proteins that function at the cilium transition zone (TZ).
Often, a single gene is linked to multiple ciliopathies with
a spectrum of phenotypes and severities.
For example, \textit{CEP290} is linked to at least six different
cilium-associated human disorders.
It is likely that these mutations do not completely abolish CEP290
function, and may be affected by genetic modifiers in an affected individual
\citep{zaghloul2010functional, khanna2009common, leitch2008hypomorphic}.
Animal models with partial loss of TZ function may therefore provide
insight on intermediate phenotypes associated with human disease.
Here, we found that reduced levels of the membrane lipid \PIP{},
which is known to be enriched at the base of cilia,
affects TZ maturation, but not assembly,
leading to hyperelongated TZs that show signs of functional defects, and
may represent one such modifier for TZ function.

In the Drosophila male germline, TZ maturation follows the initial
assembly of a nascent TZ on the basal body in the cytoplasm
followed by anchoring at the plasma membrane.
TZ maturation involves microtubule rearrangements and TZ elongation,
which leads to cilium-plasma membrane attachment.
We found that loss of \PIP{}, a membrane lipid enriched at the plasma membrane,
affects this process of TZ maturation.
It causes excessive lengthening of the TZ,
and disrupts membrane-cilium connections.

We found that the type I phosphatidylinositol 4-phosphate kinase (PIPKI) Skittles
suppresses TZ elongation in \sigd{} cells in a cilium-autonomous
manner.
We also found that cells mutant for \textit{sktl} contained hyperelongated
TZs similar to SigD-expressing cells.
Sktl also localizes to centrioles,
and our results suggest that Skittles acts locally at cilia to
regulate TZ length.
PIPKI$\gamma$ is linked to lethal congenital contractural syndrome
type 3 (LCCS3).
It has previously been suggested that LCCS3 might represent a ciliopathy.
PIPKI$\gamma$ is linked to LCCS3 with features reminiscent
of ciliopathies such as micrognathia, and a role for the LCCS1 protein
Gle1 in cilia \citep{}.
In addition, all three human PIPKI isoforms are highly expressed in testes
and PIPKI$\alpha$ and PIPKI$\beta$ are important for fertility in mice
\citep{hasegawa2012phosphatidylinositol}.

@@

\subsection{Antibodies}
The following primary antibodies were used for immunofluorescence
at the indicated concentrations -
rabbit anti-Tulp (gift from W. McGinnis \citep{ronshaugen2002structure}), 1:500;
chicken anti-GFP IgY (abcam) 1:1000;
rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
rabbit anti-Sktl (courtesy of P. Raghu), 1:500;
rabbit anti-\textit{d}Sec6 (courtesy of U. Tepass), 1:500;
mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
Secondary antibodies were Alexa 488- and Alexa 568-conjugated
anti-mouse, anti-rabbit and anti-chicken
IgG (Molecular Probes) at 1:1000.
DAPI was used to label chromatin at 1:1000.

@@

%%
%    FIGURE 1
%
\textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
\begin{enumerate}[label={(\Alph*)}, nolistsep]
\item \sigd{} expression induces Cep290 hyperelongation in mature cilia.
  Stages correspond to descriptions in \citep{cenci1994chromatin}.
\item Paired Ana1-Cep290 lengths in nascent and mature cilia.
\item \sigd{} expression induces hyperelongation of other TZ markers, such as Cby, Mks
  and acetylated tubulin.
\item TZ hyperelongation persists through meiosis but does not affect
  axoneme outgrowth.
\end{enumerate}

@@

%%
%    FIGURE 2
%
\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
\begin{enumerate}[label={(\Alph*)}, nolistsep]
\item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
\item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
  Unc-GFP.
\item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
  The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
\end{enumerate}

@@

>>>>

\documentclass[12pt, twoside, letterpaper]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage[parfill]{parskip}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{authblk}
\usepackage{charter}
\usepackage[numbers]{natbib}
\usepackage[draft]{graphicx}
\graphicspath{{../figures/}}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}

@@

\section{Discussion}
Cilia are tiny organelles that are essential for proper human development.
Many human disorders of cilia are associated with genes that encode
transition zone (TZ) proteins.
For example, mutations in the conserved TZ protein CEP290
are linked to more than 6 different ciliopathies,
ranging on a spectrum of clinical phenotypes and severities.
Most of these mutations are likely to be hypomorphic
and may be affected by genetic modifiers in affected individuals.
\citep{zaghloul2010functional, khanna2009common, leitch2008hypomorphic}.
Animal models with partial loss of TZ function may therefore
provide insight on intermediate phenotypes associated with human disease
and their cell biological basis.
In this paper, we described a novel role for the membrane lipid
phosphatidylinositol 4,5-bisphosphate (\PIP{}) in regulating TZ function.

The initial steps of ciliogenesis involve the assembly of a nascent
TZ on the basal body.
This nascent TZ ``matures'' through sequential assembly of additional
TZ proteins into a functional TZ capable of acting as a diffusion barrier
and supporting axoneme elongation and ciliary signalling.
In the Drosophila male germline, TZ maturation occurs during the
extended G2 phase in spermatocytes prior to meiosis,
and is readily observed by an increase in TZ length
and various microtubule rearrangements.
Axoneme elongation occurs in telophase II following meiosis in
spermatids, where a functional TZ detaches from the basal body
and migrates along the growing axoneme to compartmentalize the distal tip
in Cep290-dependant manner \citep{basiri2014migrating}.

We found that reduction of \PIP{} levels in the male germline by expression
of the lipid phosphatase SigD or mutation in the type I PIP kinase
Skittles (Sktl) lead to much longer TZs by the end of spermatocyte G2 phase.
Presumably, loss of \PIP{} abolishes a signal to stop TZ lengthening during
a particular step in maturation.
We were able rescue TZ hyperelongation by expression of full-length Sktl to
a large degree.
Interestingly, some cells showed cilium-autonomous suppression of lengths.
Development of the Drosophila male germline occurs in syncytial ``cysts''
of cells which share the same cytoplasm.
Therefore, our results suggest that Skittles might function \textit{in situ}
to regulate TZ maturation in these cells.

In humans, \textit{PIPKI$\gamma$} is linked to lethal congenital contractural
syndrome type 3 (LCCS3), which has been suggested to represent a ciliopathy
\citep{}.
The recent discovery of the role of LCCS1-associated GLE3 protein in cilia
further shows this.

@@

\subsection{Antibodies}
The following primary antibodies were used for immunofluorescence
at the indicated concentrations -
rabbit anti-Tulp (gift from W. McGinnis \citep{ronshaugen2002structure}), 1:500;
chicken anti-GFP IgY (abcam) 1:1000;
rat anti-RFP IgG (5F8, ChromoTek), 1:1000;
rabbit anti-Sktl (courtesy of P. Raghu), 1:500;
rabbit anti-\textit{d}Sec6 (courtesy of U. Tepass), 1:500;
mouse anti-acetylated $\alpha$-tubulin 6-11-B (Sigma-Aldrich), 1:1000.
Secondary antibodies were Alexa 488- and Alexa 568-conjugated
anti-mouse, anti-rabbit and anti-chicken
IgG (Molecular Probes) at 1:1000.
DAPI at 1:1000 was used to label chromatin.

@@

%%
%    FIGURE 1
%
\textbf{Figure 1. SigD expression induces transition zone hyperelongation.}
\begin{enumerate}[label={\Alph*.}, nolistsep]
\item Schematic diagram of the stages of ciliogenesis in the Drosophila male germline.
  Stages in brackets correspond to those from \citep{cenci1994chromatin}.
\item \sigd{} expression induces Cep290 hyperelongation in late G2 cilia.
\item Paired Ana1-Cep290 lengths in early and late G2 phase in spermatocytes.
  Numbers in red represent correlation between Cep290 and Ana1 lengths.
\item \sigd{} expression induces hyperelongation of Chibby and Mks1.
\item TZ hyperelongation persists through meiosis but does not affect
  axoneme outgrowth.
\end{enumerate}

@@

%%
%%%%
%%%    FIGURE 2
%%%
\textbf{Figure 2. Sktl is important for transition zone maturation and localizes to basal bodies.}
\begin{enumerate}[label={\Alph*.}, nolistsep]
\item Expression of full-length Sktl suppresses \sigd{}-induced TZ hyperelongation.
\item Quantification of Cep290 and Ana1 lengths from control, \sigd{} and Sktl; \sigd{} ($n$\textgreater 60) from (A).
\item \textit{sktl}$^{2.3}$ clones exhibit TZ hyperelongation. Cilia are marked using
  Unc-GFP.
\item Phylogenetic tree of PIP5Ks showing conservation of cilium-associated functions.
  The scale bar represents expected amino acid substitutions per site and branch support values are shown in red (a value of 1 indicates maximum support).
Abbreviations: Cele (\textit{Caenorhabditis elegans}), Spur (\textit{Strongylocentrotus purpuratus}), Amel (\textit{Apis mellifera}), Aaeg (\textit{Aedes aegypti}), Dana (\textit{Drosophila ananassae}), Dmel (\textit{Drosophila melanogaster}), Hsap (\textit{Homo sapiens}), Mmus (\textit{Mus musculus}), Xtro (\textit{Xenopus tropicalis}), Cint (\textit{Ciona intestinalis}), Scer (\textit{Saccharomyces cerevisiae}).
\end{enumerate}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
